Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-10-29 theory.tex
Theory of Z_p

In this equation, the parameters of average gas temperature, $T$, peripheral speed,
$v_a$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
counter-current flow ratio, $L/P$, are intrinsic to the centrifuge design.
To match the cascade design describe in \cite{glaser.2008} and \cite{walker.2017},
P1-type centrifuge properties have been chosen (Table \ref{tab:centrifuges}).

@@

>>>>

In this equation, the parameters of average gas temperature, $T$, peripheral speed,
$v_a$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
counter-current flow ratio, $L/F$, are intrinsic to the centrifuge design.
To match the cascade design describe in \cite{glaser.2008} and \cite{walker.2017},
P1-type centrifuge properties have been chosen (Table \ref{tab:centrifuges}).

@@

The variable $Z_p$ is the rectifier length, or the location of the feed point, has
an optimal axial location as defined by \cite{raetz.phd}:

\begin{equation}
    Z_p = \frac{(1-\theta)(1+L/F)}{1-\theta+L/F}Z
\end{equation}

This optimizes the recitifer length based on the cut, $\theta$, which is an expression
of the fraction of the centrifuge feed that is output as product, and the counter-current
flow, $L/F$. In practice, this value is a design parameter that is updated in the model
during the design of the centrifuge cascade.
